**Operating model**

### 2023-03-01 Rmd/omMac.Rmd
all runnuning

---
title: "**Operating model**"
subtitle: "Mackerel: Operating Model with density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
mathjax: TRUE

@@

```{r warning=FALSE, cache=FALSE, include=FALSE, knitr, eval=TRUE}

knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)

@@

iFig=0
iTab=0

library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(ggplotFL)

@@

theme_set(theme_bw(16))

source("../R/get_dropbox.R")

@@

# source("~/Desktop/projects/ddmse/R/dd.R")
source("../R/dd.R")

load(file.path(dropboxdir,"data/om/mac.RData"))

load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
ices=window(ices,start=1991)

@@

F  =propagate(window(fbar(ices),start=2020),101)
F[]=rep(c(seq(0,                               c(refpts(eq)["msy",  "harvest"]),length.out=51),
          seq(c(refpts(eq)["msy",  "harvest"]),c(refpts(eq)["crash","harvest"])*1.2,length.out=51)[-1]),each=dim(F)[2])

control=as(FLQuants("f"=F),"fwdControl")
ices   =fwd(ices,control=control,sr=eq)

dices=model.frame(FLQuants(ices[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                         "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
ggplot(dices)+
  geom_line(aes(SSB,Yield))

# Stop the clock
proc.time() - ptm

@@

```{r, vpa}

@@

```{r, vpaM}

load(file.path(dropboxdir, "data/om/parMac.RData"))
par["m1"]  =par["m1"]/10
par["w50"] =par["w50"]/1000
par["matk"]=30

@@

>>>>

---
title: "**Operating model**"
subtitle: "Mackerel: Operating Model with density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
mathjax: TRUE

@@

```{r warning=FALSE, cache=FALSE, include=FALSE, knitr, eval=TRUE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)

@@

iFig=0
iTab=0
```

```{r, pkgs}
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(ggplotFL)

@@

theme_set(theme_bw(16))
```

```{r, dropbox}
source("../R/get_dropbox.r")

@@

# source("~/Desktop/projects/ddmse/R/dd.R")
source("../R/dd.R")
```

```{r echo=FALSE, warning=FALSE, cache=FALSE, eval=TRUE}
load(file.path(dropboxdir,"data/om/mac.RData"))
```

```{r echo=FALSE, warning=FALSE, cache=FALSE, eval=TRUE}
load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
ices=window(ices,start=1991)

@@

F  =propagate(window(fbar(ices),end=2050),101)
F[]=rep(c(seq(0,                               c(refpts(eq)["msy",  "harvest"]),length.out=51),
          seq(c(refpts(eq)["msy",  "harvest"]),c(refpts(eq)["crash","harvest"])*1.2,length.out=51)[-1]),each=dim(F)[2])

control=as(FLQuants("f"=F[,-1]),"fwdControl")
ices   =fwd(propagate(ices,101),control=control,sr=eq)

dices=model.frame(FLQuants(ices[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                         "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
ggplot(dices)+
  geom_line(aes(SSB,Yield))
```

@@

```{r, vpa}
# Start the clock
ptm <- proc.time()

@@

```{r, vpaM}
# Start the clock
ptm <- proc.time()

#load(file.path(dropboxdir, "data/om/parMac.RData"))
load("/home/laurie/Desktop/projects/ddmse/data/om/parMac.RData")
par["m1"]  =par["m1"]/10
par["w50"] =par["w50"]/1000
par["matk"]=30

@@

# plot(sr)
# plot(vpaM)

### 2023-03-01 Rmd/report mac.Rmd
all runnuning

```{r}
source("../R/get_dropbox.R")

@@

```{r, echo=FALSE, fig.width=0.6, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE, eval=FALSE}

fig_nums(
  name    = "om_eqyield", level = 1, display = FALSE,
  caption = "Equilibrium curves for density dependence analyses: biomass against yield")

>>>>

```{r}
source("../R/get_dropbox.r")

@@

Introducing density-dependent process has an impact on the estimate Bmsy (calculated from Total biomass) which is shifted to the left. The expected impact on the equilibrium yield is relatively small.

```{r, echo=FALSE, fig.width=0.6, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}
fig_nums(
  name    = "om_eqyield", level = 1, display = FALSE,
  caption = "Equilibrium curves for density dependence analyses: biomass against yield")
